Sustainable computational science:\\ the ReScience initiative

### 2017-07-10 authors.tex
Small fix in affiliation
updated author information

\textbf{Benoît Girard}$^{13\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Christoph Metzner}$^{20\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},

>>>>

\textbf{Benoît Girard}$^{13\dagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Christoph Metzner}$^{20\ddagger\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
